The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-11-14 paper/model_2.tex
wordsmithing

The occurrence rate corresponding to Eq.~\ref{eq:model2_rate_density}'s rate 
density for specific mass ratios of interest $q_{\rm min} < q < q_{\rm 
max}$ is then
\begin{equation}
\Lambda|_{r_p,q_{\rm min},q_{\rm max}} = 
\frac{N_0 Z_0 + N_1 Z_1 + N_2 Z_2 f_2}
{N_{\rm tot}},
\end{equation}
for
\begin{equation}
f_2 \equiv
\int_{q_{\rm min}}^{q_{\rm max}} p_2(q) \,{\rm d}q,
\end{equation}
where $p_2(q)\propto q^\gamma$, and must be normalized to unity.

@@

\paragraph{Numerical results for Model \#2}
We first validate our model by ensuring it produces the analytically-predicted 
results for Model \#1, and the limiting case of Model \#2 described above.
Following validation, assuming ${\rm BF}=0.44$, $\alpha=3.5$, 
$\beta=\gamma=0$, and taking $Z_0=Z_1=Z_2=0.5$, we compute the true and 
apparent occurrence rates over bins in planet radius.
The results are shown in Fig.~\ref{fig:errcases_model_2}.
Evidently, dilution produces a spectrum of apparent planetary radii. This 
leads to overestimated rates everywhere except where there 
are actually planets, where the rate is underestimated by a factor of two.

>>>>

The occurrence rate corresponding to Eq.~\ref{eq:model2_rate_density}'s rate 
density for specific mass ratios of interest $q_{\rm min} < q < q_{\rm 
max}$ is then
\begin{equation}
\Lambda|_{r_p,q_{\rm min},q_{\rm max}} = 
\frac{N_0 Z_0 + N_1 Z_1 + N_2 Z_2 f_2}
{N_{\rm tot}},
\end{equation}
for
\begin{equation}
f_2 \equiv
\int_{q_{\rm min}}^{q_{\rm max}} p_2(q) \,{\rm d}q,
\end{equation}
where $p_2(q)\propto q^\gamma$, and is normalized to unity.

@@

\paragraph{Numerical results for Model \#2}
We first validate our model by ensuring it produces the analytically-predicted 
results for Model \#1, and the limiting case of Model \#2 described above.
Following validation, we assume ${\rm BF}=0.44$, $\alpha=3.5$, 
$\beta=\gamma=0$, and take $Z_0=Z_1=Z_2=0.5$. We then compute the true and 
apparent occurrence rates over bins in planet radius.
The results are shown in Fig.~\ref{fig:errcases_model_2}.
Evidently, dilution produces a spectrum of apparent planetary radii. This 
leads to overestimated rates everywhere except where at the true planet 
radius, where the rate is underestimated by a factor of two.
Compared to Model \#1 (Fig.~\ref{fig:errcases_model_1}), the general picture 
is that the apparent radius distribution is ``blurred'' by the varying 
secondary light ratios.
